The PAPER-32 power spectrum measured at several redshifts

### 2014-05-01 ms.tex
updating figures in pdf

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_10.29}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_8.54}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.94}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.68}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.55}.png}
\caption{\label{fig:pspecs} Left to right from top: power spectra centered on redshifts 10.3,8.5, 7.9, 7.7 and 7.6 (frequencies: 127, 149.5, 159.5 164.5, and 167 MHz.  All with an effective bandwidth of $\pm$10MHz which covers the redshift span $\Delta z\approx$1421MHz ($B/f^2$) which ranges from 0.8 at $z=$10.3 to 0.45 at $z=$7.4.  }
\end{figure}
\section{Results}
\label{sec:results}
\subsection{Foreground Filtering and Noise Levels}
\label{sec:noise}
The root-mean-square of the residual measures how well we've removed foregrounds.  In Figure \ref{fig:noise} we examine $T_{rms}$ as calculated by differencing between adjacent channels and between redundant baselines. We see that in the last step of coherent integration, the step between 40 second to 789 second integrations, the noise level decreases by the expected factor of $\sqrt{789/40}$.  At both stages the noise level found by both methods is roughly consistent with the theoretical level, only deviating significantly at the edges where the effective signal to noise due to the Blackman Harris window drops precipitously.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_10.29}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_8.54}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.94}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.68}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.55}.png}
\caption{\label{fig:pspecs} Left to right from top: power spectra centered on redshifts 10.3,8.5, 7.9, 7.7 and 7.6 (frequencies: 127, 149.5, 159.5 164.5, and 167 MHz.)  All with an effective bandwidth of $\pm$10MHz  covering the redshift span $\Delta z\approx$1421MHz ($B/f^2$) which ranges from 0.8 at $z=$10.3 to 0.45 at $z=$7.4.  The noise curve (blue dashes) calculated using the method described in \cite{Pober:2014p10390}  indicates the 1$\sigma$ confidence bounds on data points consisting purely of noise; 65\% of uncorrelated noise like data points will lie below the curve. Note that approximately every other $k$ bin is uncorrelated. }
\end{figure}
\section{Results}
\label{sec:results}
\subsection{Foreground Filtering and Noise Levels}
\label{sec:noise}
The root-mean-square of the residual measures how well we've removed foregrounds.  In Figure \ref{fig:noise} we examine $T_{rms}$ as calculated by differencing between adjacent channels and between redundant baselines. We see that in the last step of coherent integration, the step between 40 second to 789 second integrations, the noise level decreases by the expected factor of $\sqrt{789/40}$.  At both stages the noise level found by both methods is roughly consistent with the theoretical level, only deviating significantly at the edges where the effective signal to noise due to the Blackman Harris window drops precipitously.
